systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-02-25 paper/trunk/systemfit_summary.tex
added parks citation to the file
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@648 591db2bd-e0a0-4d22-8c19-2192dbb7da31
updated the unbalanced section.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@649 591db2bd-e0a0-4d22-8c19-2192dbb7da31

\subsubsection*{Unbalanced datasets}
Currently, the \pkg{systemfit} package requires
that all equations have the same number of observations.
However, many data sets have unbalanced observations.%
\footnote{
For instance,
forestry datasets typically contain observations of many inexpensive
observations (stem diameter) and few expensive observations such
as stem height.
}
Simply dropping data points
that do not contain observations for all equations
may considerably reduce the number of observations,
and thus, the information utilized in the estimation.
Hence, it is our intention to include the capability for estimations
with unbalanced data sets as described in \citet{schmidt77}
in future releases of \pkg{systemfit}.

\subsubsection*{Serial correlation and heteroscedasticity}
For all of the methods developed in the package, the disturbances of
the individual equations are assumed to be independent and identically
distributed (iid).
The package could be enhanced by the inclusion of methods to fit
equations with serially correlated and heteroscedastic disturbances
(parks, 1967).

@@

\subsubsection*{Non-linear estimation}
Finally, the \pkg{systemfit} package provides a function to estimate
systems of non-linear estimations.
However, the function \code{nlsystemfit} is currently under
development and the results are not yet always reliable due to
convergence difficulties.
% We hope to improve this behavior soon.

%% testing for the new svn repos
%% It works great!!!

>>>>

\subsubsection*{Unbalanced datasets}
Currently, the \pkg{systemfit} package requires
that all equations have the same number of observations.
However, many data sets have unbalanced observations.%
\footnote{
For instance,
forestry datasets typically contain many observations of inexpensive
variables (stem diameter, tree count) and few expensive variables such
as stem height or volume.
}
Simply dropping data points that do not contain observations for all
equations may reduce the number of observations considerably, and
thus, the information utilized in the estimation.
Hence, it is our intention to include the capability for estimations
with unbalanced data sets as described in \citet{schmidt77} in future
releases of \pkg{systemfit}.

\subsubsection*{Serial correlation and heteroscedasticity}
For all of the methods developed in the package, the disturbances of
the individual equations are assumed to be independent and identically
distributed (iid).
The package could be enhanced by the inclusion of methods to fit
equations with serially correlated and heteroscedastic disturbances
\citep{parks67}.

@@

\subsubsection*{Non-linear estimation}
Finally, the \pkg{systemfit} package provides a function to estimate
systems of non-linear estimations.
However, the function \code{nlsystemfit} is currently under
development and the results are not yet always reliable due to
convergence difficulties.
